Multitasking Interfaces on Touchscreen Mobile Devices

### 2015-12-09 sigchi-latex-proceedings 2/final-paper.tex
Add Experimental Design

\subsection{Experimental Design}
The experiment had a one-way within-subject design with the multitasking interface (stacked and non-stacked) acting as a two-level independent variable. Order effects were counterbalanced by switching the order of testing with two groups of participants. The first group tested the stacked interface first, while the second group tested the non-stacked interface first. Time to completion and accuracy served as the dependent variables. Participants performed the set of tasks twice for each stacked and non-stacked multitasking interfaces with two different experimenters.

@@

We designed the tasks to cover the three most common interactions with the multitasking interface. Firstly, minimal, where the participant’s interaction with the multitasking interface is limited to one or two switches. Second, a longer but real-world representative task where the participant switched between three or more apps. Last, repetitive switching, a common scenario where the participant repeatedly switched between two apps to achieve a specified goal. Combined with a within-subject design where the participant performs these tasks multiple times on each level gave us a  comprehensive set of data points to test the hypotheses.

@@

Each participant performed three blocks of tasks twice, once on each multitasking interface. There were six trials in total per participant. Each participant was handed a sheet outlining all the tasks. The participant read each block of tasks and executed them in the order listed on the sheet. Each block was preceded by a short break for the experimenter to setup the device. The participant completed the tasks at his/her own pace. At the commencement of the experiment, the participant completed an exit survey. The whole experiment took about 20 minutes to complete per participant.

>>>>

\subsection{Experimental Design}
The experiment had a one-way within-subject design with the multitasking interface (stacked and non-stacked) acting as a two-level independent variable. Order effects were counterbalanced by switching the order of testing with two groups of participants. The first group tested the stacked interface first on the Lollipop phone, while the second group tested the non-stacked interface first on the KitKat phone. Time to completion and accuracy served as the dependent variables. Participants performed the set of tasks twice for each stacked and non-stacked multitasking interfaces with two different experimenters.

@@

@@

Each task was designed to cover one of three common interactions. First was a minimal interaction, where the application switches was limited to one or two switches between three open applications. Second was a longer task where the participant switched between three or more applications. In this task, participants had to scroll through the multitasking interface, which presented a non-ordered list of apps to find the app they were to switch to. Last was a repetitive switching task, a common scenario where the participant repeatedly switched between two apps to achieve a specified goal. Combined with a within-subject design where the participant performs these tasks multiple times on each level gave us a comprehensive set of data points to test the hypotheses.

Each participant executed each block twice, once on each multi-tasking interface (stacked and non-stacked). There were six trials in total per participant. Each participant was handed a sheet outlining all the tasks for each block. Each block of tasks was preceded by a short break for the experimenter to setup the device and demonstrate the tasks, if requested by the participant. Participants were instructed to begin tasks and were observed for any errors. Errors were recorded as a total per task block. Tasks were completed at the participant's? own pace and errors (if any) were corrected at their discretion. Experimenter logged the data for each block of tasks on each interface. At the commencement of the experiment, the participant completed an exit survey. The whole experiment took about 20 minutes to complete per participant.
